### 2020-05-31 paper.tex
Edit Introduction & Abstract

\title{Improved Global Routing Using A-Star Algorithm\\}

@@

\author{\IEEEauthorblockN{AbdElrahman Elshafei\IEEEauthorrefmark{1}, Hossam Ahmed\IEEEauthorrefmark{2}, Mahmoud Mohamed\IEEEauthorrefmark{3} and Muhanad Atef\IEEEauthorrefmark{4}}
\IEEEauthorblockA{Computer Engineering Dept.,
Faculty of Engineering, Cairo University\\
Cairo, Egypt\\
\IEEEauthorrefmark{1}abdelrahman.elshafei98@gmail.com,
\IEEEauthorrefmark{2}hossamahmed201515@gmail.com,
\IEEEauthorrefmark{3}mmmacmp@gmail.com,
\IEEEauthorrefmark{4}muhanad.atef23@gmail.com}}

@@

\begin{abstract}
    In this paper we want to improve routing by improving global routing, this can be done by using A-Star algorithm, which will reduce time taken in this process and achieve the minimum wire length, many comparisons are taken in this paper with different algorithms to find the optimum algorithm to be used to achieve both minimum wire length and minimum time taken. From the comparisons of the paper we can find that using any algorithm is a trade off as when we decrease time taken, the wire length is increased and vice versa, so we cannot find an algorithm which is better from the other algorithms in general but we can say that using A-Star algorithm is a good approach to be used in global routing as it decreases the routing time however it is not the the best achieveable time but it is better than many other algorithms, and it is the best algorithm to achieve the minimum wire length with this complexity.
\end{abstract}

@@

Routing is critical step in physical design process. Until now the optimum solution for VLSI routing has not been achieved yet, so it is considered as a very interesting challenging feild. It is exactly done in two steps, global routing and detailed routing. At first global routing is run which is the responsible for making an approximate routing for the whole circuit in order to be used as a guide for detailed routing, then the detailed routing is run to make the exact routing for the system. That means if global or detailed routing is improved the whole routing process is improved, but there are many problems we have to overcome to make a correct routing process. First of all we have to take into consideration the scale, as millions of wires exist in a small chip area which means that many kilometers of wires are placed in a very small area, so we have to minimize total wire length as much as we can, also we know that as the wire length increases the resistance increases as well which means more delay in the chip. We can find another problem as circuits are made in nano-scale which means that its geometric will be complex. Another problem that routing algorithm have to be applicable for more than one layer with different costs. We also have to take into consideration the direction of wires in every layer (vertical | horizontal) and no diagonal pathes, then to go from source 'S' to target 'T' the path taken should be in (vertical | horizontal) directions thet specified by the layer (at each layer wires are placed in one direction only), then there is another problem as when a wire goes from layer to another to continue on the perpendicular direction it have to go through via which have a high resistance. DFM (design for manufacturer) rules also has to be achieved. All of these constraints must be taken into consideration with the global routing to achieve hundred percent of the circuit connections, that means global routing will take a lot of time to achieve all these constraints, and here is the challenge to achieve all the routing specifications with minimum time taken.

@@

    \node [box,fill=green] at (0,0.5){A};
    \node[box,fill=green  ] at (2,2){A};  
    \node[box,fill=green  ] at (0,1){};  
    \node[box,fill=green  ] at (0,1.5){};  
    \node[box,fill=green  ] at (0,2){};  
    \node[box,fill=green  ] at (0.5,2){};  
    \node[box,fill=green  ] at (1,2){};  
    \node[box,fill=green  ] at (1.5,2){};  
    \node[box,fill=red  ] at (1.5,2.5){B}; 
    \node [box,fill=red] at (2.5,0.5){B}; 
    \node [box,fill=red] at (2.5,1){};
    \node [box,fill=red] at (2.5,1.5){};
    \node [box,fill=red] at (2.5,2){};
    \node [box,fill=red] at (2.5,2.5){};
    \node [box,fill=red] at (2,2.5){};
    \end{tikzpicture}
}
\caption{Global routing to get the best pathes}
\label{fig:GlobalRoutingProcess}
\end{figure}

Figure~\ref{fig:GlobalRoutingProcess} shows a very simple approach of how the global router works. At (a) the source and target of both (A,B) need to be connected ignoring obstacles, nevertheless we can observe that the global router have to iterate to get the best routing pathes, at (b) (B,B) connected but there is no way to connect (A,A) as when (B,B) connected together they blocked the way for (A,A) to be connected, after some iterations we can find the figure at (c) in which (A,A) and (B,B) connected correctly, but there is a problem, the (A,A) connection is not the optimal path as there are pathes which achieve less wire length, so the global router have to iterate until reaching the optimal path. These iterations are done for only two connections in one layer without obstacles, then how about millions of wires in VLSI? this shows how much the global routing algorithm has to be very fast in order to connect this huge number of wires as fast as possible.

@@

Several papers proposed various types of approaches to improve the overall efficiency of the multilevel feedback queue scheduling algorithm. The chosen quantum time for each queue plays a major role. Hence, it is essential to choose a proper method to compute the time quantum value to minimize response time and maximize overall performance. In , an algorithm is introduced for minimizing the response time. In this algorithm, a Recurrent Neural Network (RNN) is used to determine both the number of queues and the optimized time quantum value for each queue. The RNN generates an effective model to compute the time quantum value. Their proposed intelligent version of the MLFQ offers good results, however, it suffers from a few drawbacks, the first being the direct proportionality of its network learning time and the amount of input data, and the second is the possibility of experiencing initial overhead at the first iterations of the algorithm. Our approach proposes an improved version of MLFQ that utilizes an altered version of RR named shortest remaining burst round-robin (SRBRR) introduced in  which avoids the cost of learning time and overhead time in . Regarding the various approaches to improve the MLFQ algorithm, those attempts dealt with starvation by assigning different quantum values to the ready queues depending on their priority. Our approach also deals with starvation by boosting processes from lower priority queues to higher ones according to certain criteria.

@@

>>>>

\title{Improved Global Routing By Using A Star Algorithm\\}

@@

\author{\IEEEauthorblockN{Abdulrahman Khalid\IEEEauthorrefmark{1}, Hossam Ahmed\IEEEauthorrefmark{2}, Mahmoud Mohamed\IEEEauthorrefmark{3} and Muhanad Atef\IEEEauthorrefmark{4}}
\IEEEauthorblockA{Computer Engineering Dept.,
Faculty of Engineering, Cairo University\\
Cairo, Egypt\\
\IEEEauthorrefmark{1}abdulrahman.elshafei98@gmail.com,
\IEEEauthorrefmark{2}hossamahmed201515@gmail.com,
\IEEEauthorrefmark{3}mmmacmp@gmail.com,
\IEEEauthorrefmark{4}muhanad.atef23@gmail.com}}

@@

\begin{abstract}
    In this paper VLSI routing is improved by improving global routing, this can be done by using A-Star with heuristic cost function that has parameters which affect the time taken by the router on changing instead of Dijkstra's algorithm in finding path, which will reduce time taken in this process and achieve the minimum wirelength, many comparisons are taken in this paper with different algorithms to find the optimum algorithm to be used to achieve both minimum wirelength and minimum time taken. From the comparisons of the paper we can find that using any algorithm is a trade off as when time taken is decreased, the wirelength is increased and vice versa, so there is no algorithm which is better from the other algorithms in general but using A-Star algorithm with the heuristic function in finding path is a good approach to be used in global routing as it decreases the routing time and achieve the minimum wirelength.
\end{abstract}

@@

Routing is critical step in physical design process. Until now the optimum solution for VLSI routing has not been achieved yet, so it is considered as a very interesting challenging field. It is exactly done in two steps, global routing and detailed routing. At first global routing is run which is the responsible for making an approximate routing for the whole circuit in order to be used as a guide for detailed routing, then the detailed routing is run to make the exact routing for the system. That means if global or detailed routing is improved the whole routing process is improved, but there are many problems that have to be overcame to make a correct routing process. First of all the scale has to be taken into consideration, as millions of wires exist in a small chip area which means that many kilometers of wires are placed in a very small area, so wetotal wirelength has to be minimized as much as possible, also it is known that as the wirelength increases the resistance increases as well which means more delay in the chip. There is another problem as circuits are made in nano-scale which means that its geometric will be complex. Another problem is that routing algorithm have to be applicable for more than one layer with different costs. The direction of wires also have to taken into consideration as the direction of wires in every layer can be either vertical or horizontal and no diagonal paths, then to go from source 'S' to target 'T' the path taken should be in (vertical | horizontal) directions that specified by the layer (at each layer wires are placed in one direction only), then there is another problem as when a wire goes from layer to another to continue on the perpendicular direction it have to go through via which have a high resistance. DFM (design for manufacturer) rules also has to be achieved. All of these constraints must be taken into consideration with the global routing to achieve hundred percent of the circuit connections, that means global routing will take a lot of time to achieve all these constraints, and here is the challenge to achieve all the routing specifications with minimum time taken.

@@

    \node [box,fill=green] at (0,0.5){A};
    \node[box,fill=green  ] at (2,2){A};  
    \node[box,fill=green  ] at (0,1){};  
    \node[box,fill=green  ] at (0,1.5){};  
    \node[box,fill=green  ] at (0,2){};  
    \node[box,fill=green  ] at (0.5,2){};  
    \node[box,fill=green  ] at (1,2){};  
    \node[box,fill=green  ] at (1.5,2){};  
    \node[box,fill=red  ] at (1.5,2.5){B}; 
    \node [box,fill=red] at (2.5,0.5){B}; 
    \node [box,fill=red] at (2.5,1){};
    \node [box,fill=red] at (2.5,1.5){};
    \node [box,fill=red] at (2.5,2){};
    \node [box,fill=red] at (2.5,2.5){};
    \node [box,fill=red] at (2,2.5){};
    \end{tikzpicture}
}
\caption{Finding path in global routing}
\label{fig:GlobalRoutingProcess}
\end{figure}

Figure~\ref{fig:GlobalRoutingProcess} shows a very simple approach of how the global router works. At (a) the source and target of both (A,B) need to be connected ignoring obstacles, nevertheless we can observe that the global router have to iterate to get the best routing paths, at (b) (B,B) connected but there is no way to connect (A,A) as when (B,B) connected together they blocked the way for (A,A) to be connected, after some iterations we can find the figure at (c) in which (A,A) and (B,B) connected correctly, but there is a problem, the (A,A) connection is not the optimal path as there are paths which achieve less wirelength, so the global router have to iterate until reaching the optimal path. These iterations are done for only two connections in one layer without obstacles, then how about millions of wires in VLSI? this shows how much the global routing algorithm has to be very fast in order to connect this huge number of wires as fast as possible.

@@

Several papers proposed various types of approaches to improve the routing process, each of them tried to improve the overall routing by improving one or more parameters, some paperes tried to decrease number of vias, other papers tried to decrease the time taken and so on. In \cite{b2} they used two bounded length maze algorithms as finding path algorithms in order to make the router faster, the first one is optimal-BLMR which is used to get the minimum cost paths to be used as a routing paths, this can be done in three steps, first BLC (bounded length constraint) is defined as grater than Manhattan distance then to go from source to target the neighbour points are tested if it can be a part of path or not, each point that violates the BLC constraint is discarded, second

@@

\bibitem{b2} Liu, Wen-Hao, et al. "NCTU-GR 2.0: Multithreaded collision-aware global routing with bounded-length maze routing." \textit{IEEE Transactions on computer-aided design of integrated circuits and systems} 32.5 (2013): 709-722.
